Operational Performance Analyses at European Airports with Community-Collected Open Data

### 2020-03-04 paper01.Rmd
background updated with status/role of data

---
title: "Operational Performance Analyses at European Airports with Community-Collected Open Data"
author: "RQ"
date: "02/02/2020"
output:
  bookdown::pdf_document2: default
  html_document:
    df_print: paged
  word_document: default
abstract: My abstract
bibliography: paperxx.bib
---

@@

@@

This paper is fully reproducible. The underlying Rmarkdown file, the supporting data preparatory and analytical scripts are available at:

>>>>

---
title: "Operational Performance Analyses at European Airports with Community-Collected Open Data"
author: "RQ"
date: "02/02/2020"
output:
  bookdown::pdf_document2:
    toc: false
  html_document:
    df_print: paged
  word_document: default
abstract: My abstract
bibliography: paperxx.bib
---

@@

While there never existed a disagreement about the fact that air transport / air traffic engineering requires access to data for developing advanced models or verify and validate reported results, the actual access to the data is traditionally sparse.
The status and access to data in air transportation research has been analysed by @bourgois_2014.

@@

This paper is fully reproducible. The underlying Rmarkdown file, the supporting data preparatory and analytical scripts are available at: https://github.com/rainer-rq-koelle/paper-2020-ICNS.
